### 2024-06-27 misc/expo/kelleymeka.tex
Added many photos

It is easy to check that if $\mu$ has $\norm{\mu}_1 = 1$, then so does $\mu*\mu$ and $\mu\circ\mu$.
We shall say that $\mu:G\to \RR_{\ge 0}$ is a {\it probability measure} on $G$ if $\norm{\mu}_1 = 1$. The
following proposition concerns such measures.

\edef\normonefourier{\the\thmcount}
\proclaim Proposition \advthm. Let $G$ be a finite abelian group.
If $\mu:G\to \RR_{\ge 0}$ is a probability measure, then
$$ \hat{\mu-1} = \hat \mu (1-\one_{\chi_0}).$$

\proof We expand
$$\eqalign{
\hat{\mu-1}(\chi) &=  \ex_{x\in G} \bigl(\mu(x)-1\bigr) \chi(-x) \cr
&= \ex_{x\in G} \mu(x)\chi(-x) - \ex_{x\in G} \chi(-x).\cr
&= \hat\mu(\chi) - \ex_{x\in G} \chi(-x).\cr
}$$
If $\chi\ne\chi_0$, then the expectation vanishes, and
if $\chi = \chi_0$, then the expection clearly equals $1$, and $\mu(\chi_0) = \norm{\mu}_1 = 1$, so the whole
expression is zero.\slug

If $\mu:G\to \RR_{\ge 0}$ is a probability measure and $f,g:G\to \CC$ we write
$$\langle f,g\rangle_\mu = \ex_{x\in G} \mu(x)f(x)\bar{g(x)}$$
for the inner product relative to $\mu$, and for $1\le p<\infty$ we write
$$\norm{f}_{p(\mu)} = \Bigl( \ex_{x\in G} \mu(x) \bigl| f(x)\bigr|^p \Bigr)^{1/p}$$
for the $L_p$ norm relative to $\mu$. The following basic proposition establishes the monotonicity of
$L_p$ norms with respect to $p$.

\edef\monotonenorm{\the\thmcount}
\parenproclaim Proposition~{\advthm} (Monotonicity of $L_p$ norms). Let $G$ be a finite abelian group.
Let $\mu:G\to \RR_{\ge 0}$ be a probability measure and let $f:G\to \CC$.
For $1\le p<q<\infty$, we have
$$\norm{f}_{p(\mu)} \le \norm{f}_{q(\mu)}.$$

@@

For convenience, when $\mu:G\to \RR_{\ge 0}$ is a probability measure and $X\subseteq G$, we write
$$\mu(X) = \norm{\one_X}_{1(\mu)} = \ex_{x\in G} \mu(x) \one_X(x),$$
and refer to this quantity as the {\it density of $X$ relative to $\mu$}.

@@

\proof Let $S' = \bigl\{x\in G : (\mu_A\circ\mu_A)(x) > (1+\eps)\norm{\mu_A\circ\mu_A}_p\bigr\}$, and apply
Lemma~{\dependentrandom} with the same $p$ and $\eps$, but $\delta$ set to $\eps/8$, $S$ set to $S'$,
and $B_1 = B_2 = G$ so that $\mu = \mu_{B_1} = \mu_{B_2}$ is the uniform measure on $G$. Hence the
sets $A_1$ and $A_2$ given by the lemma will each have density
$$\Omega\bigl((\alpha(1+\eps))^{2p+O(\eps^{-1}\log(8/\eps))}\bigr)
=\Omega\bigl(\alpha^{2p+O(\eps^{-1}\log(\eps^{-1}))}\bigr)$$
in $G$, and since
$$(1-\eps)\norm{\mu_A\circ\mu_A}_p \ge (1-\eps)(1+\eps) = 1-\eps^2 \ge 1-\eps/2,$$
we have $S'\subseteq S$ and thus
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle \ge
\langle \mu_{A_1}\circ\mu_{A_2}, \one_{S'}\rangle \ge 1-\eps/8.\noskipslug$$

@@

\proof Suppose that (i) fails. Then by Lemma~{\holderlifting} there is some $p = O\bigl(\log(1/\gamma)\bigr)$
such that $\norm{\mu_A\circ\mu_A - 1}_p\ge \eps/ 2$. By the second convolution law (part (ii) of
Proposition~{\convolutions}), $\mu_A\circ\mu_A$ is a nonnegative function, and note also that if
$\nu$ is the uniform measure on $\FF_q^n$, then for any $\chi:\hat{\FF_q^n}\to \CC$,
$$\hat\nu(\chi) = \ex_{x\in G} \nu(x)\chi(-x) = \cases{q^{-n}, & if $\chi$ is the trivial character;
\cr 0, & otherwise.}$$
This implies in particular that $\hat\nu \ge 0$,
so by Lemma~{\unbalancing} applied with $f=\mu_A\circ\mu_A$ and the uniform measure for $\nu$, we find
that $\norm{\mu_A\circ\mu_A}_{p'}\ge 1+\eps/4$ for some
$p' = O\bigl((2/\eps)\log(2/\eps) p\bigr)= O\bigl(\eps^{-1}\log(\eps^{-1})\log(1/\gamma)\bigr)$.
Let $C(\eps) = \eps^{-1}\log(\eps^{-1})$. By Corollary~{\deprandcorollary},
there are sets $A_1,A_2\subseteq G$, each of density
$\Omega(\alpha^{2p'+O(C(\eps))})$, such that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle \ge 1 - \eps/32,$$
where $S = \bigl\{ x \in G:(\mu_A\circ\mu_A)(x)\ge 1+\eps/8\bigr\}$. Feeding $-A_1$, $A_2$, and $S$
into Theorem~{\almostperiodicity} with $\eps/32$ gives us a subspace $V$ of codimension
$$\eqalign{
O\Bigl(\eps^{-2}&\log\bigl(\eps^{-1}\alpha^{-2p'-O(C(\eps))}\bigr)^2
\log\bigl(\alpha^{-2p'-O(C(\eps))}\bigr)^2\Bigr) \cr
&= O\Bigl(\eps^{-2} (2p'+C(\eps))^2\log(1/\alpha)^2
\bigl((2p'+C(\eps))\log(1/\alpha)+\log(\eps^{-1})\bigr)^2
\Bigr)\cr
&=O\Bigl(\eps^{-2}\bigl(\log(1/\gamma)+C(\eps)\bigr)^4\log(1/\alpha)^4\Bigr) \cr
}$$
such that
$$\bigl| \langle \mu_V*\mu_{-A_1}*\mu_{A_2}, \one_S\rangle -
 \langle \mu_{-A_1}*\mu_{A_2}, \one_S\rangle\bigr| \le \eps/32.$$
It is easily checked that $\mu_{-A_1}*\mu_{A_2} = \mu_{A_1}\circ\mu_{A_2}$, so we find that
$$\bigl\langle \mu_V*(\mu_{A_1}\circ\mu_{A_2}), \one_S\bigr\rangle \ge 1-\eps/16.$$
Now we observe that
$$\bignorm{(\mu_{A_1}\circ\mu_{A_2})\circ\mu_{A_2}}_1
= \ex_{z\in G}\mu_{A_1}(z)\ex_{y\in G} \mu_{A_2}(y+z) \ex_{x\in G} \mu_A(x+y) = 1,$$
so that,
$$\eqalign{
\max_{x\in G}\;(\mu_V*\one_A)(x) &= \alpha\max_{x\in G}\;(\mu_V*\mu_A)(x) \cr
&= \alpha \bignorm{(\mu_{A_1}\circ\mu_{A_2})\circ\mu_A}_1 \max_{x\in G}\;(\mu_V*\mu_A)(x)\cr
&\ge \alpha\bigl\langle \mu_V*\mu_A, (\mu_{A_1}\circ\mu_{A_2})\circ\mu_A\bigr\rangle\cr
&= \alpha\bigl\langle \mu_V*\mu_A * (\mu_{A_1}\circ\mu_{A_2}), \mu_A\bigr\rangle\cr
&= \alpha\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \mu_A\circ\mu_A\bigr\rangle,\cr
}$$
where in the last two lines we have employed the adjoint property
$\langle f,g*h \rangle = \langle h\circ f,g\rangle$, as well as the commutative properties
$f*g = g*f$ and $\langle f,g\rangle = \langle g,f\rangle$,
all of which hold for functions $f,g,h : G\to \RR$. But by the construction of $S$, we have
$\one_S(x)(\mu_A\circ\mu_A)(x) \ge (1+\eps/8)\one_S$, so
$$\eqalign{
\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \mu_A\circ\mu_A\bigr\rangle
&\ge \bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \one_S(\mu_A\circ\mu_A)\bigr\rangle \cr
&\ge (1+\eps/8)\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \one_S\bigr\rangle \cr
&\ge (1+\eps/8)(1-\eps/16) \cr
&\ge 1+\eps/32, \cr
}$$
hence we conclude that
$$\max_{x\in G}\;(\one_A*\mu_V)(x) \ge (1+\eps/32)\alpha\noskipslug$$

>>>>

It is easy to check that if $\mu$ has $\norm{\mu}_1 = 1$, then so does $\mu*\mu$ and $\mu\circ\mu$.
The following proposition concerns functions with this $1$-norm.

\edef\normonefourier{\the\thmcount}
\proclaim Proposition \advthm. Let $G$ be a finite abelian group.
If $\mu:G\to \RR_{\ge 0}$ has $\norm{\mu}_1 = 1$, then
$$ \hat{\mu-1} = \hat \mu (1-\one_{\chi_0}).$$

\proof We expand
$$\eqalign{
\hat{\mu-1}(\chi) &=  \ex_{x\in G} \bigl(\mu(x)-1\bigr) \chi(-x) \cr
&= \ex_{x\in G} \mu(x)\chi(-x) - \ex_{x\in G} \chi(-x).\cr
&= \hat\mu(\chi) - \ex_{x\in G} \chi(-x).\cr
}$$
If $\chi\ne\chi_0$, then the expectation vanishes, and
if $\chi = \chi_0$, then the expectation
clearly equals $1$, and $\mu(\chi_0) = \norm{\mu}_1 = 1$, so the whole
expression is zero.\slug

For $\mu:G\to \RR_{\ge 0}$ with $\norm{\mu}_1 = 1$ and arbitrary $f,g:G\to \CC$ we write
$$\langle f,g\rangle_\mu = \ex_{x\in G} \mu(x)f(x)\bar{g(x)}$$
for the inner product relative to $\mu$, and for $1\le p<\infty$ we write
$$\norm{f}_{p(\mu)} = \Bigl( \ex_{x\in G} \mu(x) \bigl| f(x)\bigr|^p \Bigr)^{1/p}$$
for the $L_p$ norm relative to $\mu$. The following basic proposition establishes the monotonicity of
$L_p$ norms with respect to $p$.

\edef\monotonenorm{\the\thmcount}
\parenproclaim Proposition~{\advthm} (Monotonicity of $L_p$ norms). Let $G$ be a finite abelian group.
Let $\mu:G\to \RR_{\ge 0}$ have $\norm{\mu}_1 = 1$ and let $f:G\to \CC$.
For $1\le p<q<\infty$, we have
$$\norm{f}_{p(\mu)} \le \norm{f}_{q(\mu)}.$$

@@

For convenience, when $\mu:G\to \RR_{\ge 0}$ has $\norm{\mu}_1 = 1$ and $X\subseteq G$, we write
$$\mu(X) = \norm{\one_X}_{1(\mu)} = \ex_{x\in G} \mu(x) \one_X(x),$$
and refer to this quantity as the {\it density of $X$ relative to $\mu$}.

@@

\proof Let $S' = \bigl\{x\in G : (\mu_A\circ\mu_A)(x) > (1+\eps)\norm{\mu_A\circ\mu_A}_p\bigr\}$, and apply
Lemma~{\dependentrandom} with the same $p$ and $\eps$, but $\delta$ set to $\eps/8$, $S$ set to $S'$,
and $B_1 = B_2 = G$ so that $\mu = \mu_{B_1} = \mu_{B_2}$ is the constant function $1$ on $G$. Hence the
sets $A_1$ and $A_2$ given by the lemma will each have density
$$\Omega\bigl((\alpha(1+\eps))^{2p+O(\eps^{-1}\log(8/\eps))}\bigr)
=\Omega\bigl(\alpha^{2p+O(\eps^{-1}\log(\eps^{-1}))}\bigr)$$
in $G$, and since
$$(1-\eps)\norm{\mu_A\circ\mu_A}_p \ge (1-\eps)(1+\eps) = 1-\eps^2 \ge 1-\eps/2,$$
we have $S'\subseteq S$ and thus
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle \ge
\langle \mu_{A_1}\circ\mu_{A_2}, \one_{S'}\rangle \ge 1-\eps/8.\noskipslug$$

@@

\proof Suppose that (i) fails. Then by Lemma~{\holderlifting} there is some $p = O\bigl(\log(1/\gamma)\bigr)$
such that $\norm{\mu_A\circ\mu_A - 1}_p\ge \eps/ 2$. By the second convolution law (part (ii) of
Proposition~{\convolutions}), $\mu_A\circ\mu_A$ is a nonnegative function, and note also that if
$\nu$ is the constant function $1$ on $\FF_q^n$, then for any $\chi:\hat{\FF_q^n}\to \CC$,
$$\hat\nu(\chi) = \ex_{x\in G} \nu(x)\chi(-x) = \cases{1, & if $\chi$ is the trivial character;
\cr 0, & otherwise.}$$
This implies in particular that $\hat\nu \ge 0$,
so by Lemma~{\unbalancing} applied with $f=\mu_A\circ\mu_A$ and the constant function $1$ for $\nu$, we find
that $\norm{\mu_A\circ\mu_A}_{p'}\ge 1+\eps/4$ for some
$p' = O\bigl((2/\eps)\log(2/\eps) p\bigr)= O\bigl(\eps^{-1}\log(\eps^{-1})\log(1/\gamma)\bigr)$.
Let $C(\eps) = \eps^{-1}\log(\eps^{-1})$. By Corollary~{\deprandcorollary},
there are sets $A_1,A_2\subseteq G$, each of density
$\Omega(\alpha^{2p'+O(C(\eps))})$, such that
$$\langle \mu_{A_1}\circ\mu_{A_2}, \one_S\rangle \ge 1 - \eps/32,$$
where $S = \bigl\{ x \in G:(\mu_A\circ\mu_A)(x)\ge 1+\eps/8\bigr\}$. Feeding $-A_1$, $A_2$, and $S$
into Theorem~{\almostperiodicity} with $\eps/32$ gives us a subspace $V$ of codimension
$$\eqalign{
O\Bigl(\eps^{-2}&\log\bigl(\eps^{-1}\alpha^{-2p'-O(C(\eps))}\bigr)^2
\log\bigl(\alpha^{-2p'-O(C(\eps))}\bigr)^2\Bigr) \cr
&= O\Bigl(\eps^{-2} (2p'+C(\eps))^2\log(1/\alpha)^2
\bigl((2p'+C(\eps))\log(1/\alpha)+\log(\eps^{-1})\bigr)^2
\Bigr)\cr
&=O\Bigl(\eps^{-2}\bigl(\log(1/\gamma)+C(\eps)\bigr)^4\log(1/\alpha)^4\Bigr) \cr
}$$
such that
$$\bigl| \langle \mu_V*\mu_{-A_1}*\mu_{A_2}, \one_S\rangle -
 \langle \mu_{-A_1}*\mu_{A_2}, \one_S\rangle\bigr| \le \eps/32.$$
It is easily checked that $\mu_{-A_1}*\mu_{A_2} = \mu_{A_1}\circ\mu_{A_2}$, so we find that
$$\bigl\langle \mu_V*(\mu_{A_1}\circ\mu_{A_2}), \one_S\bigr\rangle \ge 1-\eps/16.$$
Now we observe that
$$\bignorm{(\mu_{A_1}\circ\mu_{A_2})\circ\mu_{A_2}}_1
= \ex_{z\in G}\mu_{A_1}(z)\ex_{y\in G} \mu_{A_2}(y+z) \ex_{x\in G} \mu_A(x+y) = 1,$$
so that,
$$\eqalign{
\max_{x\in G}\;(\mu_V*\one_A)(x) &= \alpha\max_{x\in G}\;(\mu_V*\mu_A)(x) \cr
&= \alpha \bignorm{(\mu_{A_1}\circ\mu_{A_2})\circ\mu_A}_1 \max_{x\in G}\;(\mu_V*\mu_A)(x)\cr
&\ge \alpha\bigl\langle \mu_V*\mu_A, (\mu_{A_1}\circ\mu_{A_2})\circ\mu_A\bigr\rangle\cr
&= \alpha\bigl\langle \mu_V*\mu_A * (\mu_{A_1}\circ\mu_{A_2}), \mu_A\bigr\rangle\cr
&= \alpha\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \mu_A\circ\mu_A\bigr\rangle,\cr
}$$
where in the last two lines we have employed the adjoint property
$\langle f,g*h \rangle = \langle h\circ f,g\rangle$, as well as the commutative properties
$f*g = g*f$ and $\langle f,g\rangle = \langle g,f\rangle$,
all of which hold for functions $f,g,h : G\to \RR$. But by the construction of $S$, we have
$\one_S(x)(\mu_A\circ\mu_A)(x) \ge (1+\eps/8)\one_S$, so
$$\eqalign{
\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \mu_A\circ\mu_A\bigr\rangle
&\ge \bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \one_S(\mu_A\circ\mu_A)\bigr\rangle \cr
&\ge (1+\eps/8)\bigl\langle \mu_V* (\mu_{A_1}\circ\mu_{A_2}), \one_S\bigr\rangle \cr
&\ge (1+\eps/8)(1-\eps/16) \cr
&\ge 1+\eps/32, \cr
}$$
hence we conclude that
$$\max_{x\in G}\;(\one_A*\mu_V)(x) \ge (1+\eps/32)\alpha\noskipslug$$
